---
title: "Portfolio Analysis" 
author: "`r paste0('for ', params$pFundID, ' as of ')`"
date: "`r params$pQtrEnd`"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
params:
  pFundID: "EHF2"
  pQtrEnd: "September 30, 2022"
---

```{r label="setup", echo=FALSE}

knitr::opts_chunk$set(echo = TRUE, error=FALSE, warning=TRUE)
options(dplyr.summarise.inform = FALSE)

```


```{r label="library-definitions", echo=FALSE}

# R Package Definitions                                       
library(tidyverse)
library(lubridate)
library(tidyquant)  
library(dplyr)
library(scales)
library(forcats)
library(openxlsx)
library(flextable)
library(echarts4r)
library(flextable)

# set the working directory for the input / output files
myDirectory <- "~/Dropbox/UC-Unclutter/AA My R Stuff/RPortfolio"
setwd(myDirectory)

# load the input file that was created by Portfolio Analysis
# Note: this is an rda file that contains several file including:
#  dfProjAll        - the full dataframe of all project information
#  dfChart1Data     - the dataframe used in this RMarkdown Analysis
#  dfEHF1Totals     - Stats for EHF1
#  dfEHF2Totals     - Stats for EHF2
idf_ProjAll <- paste0(myDirectory,"/03 df Files/dfProjAll.rda")
load(idf_ProjAll)

# This will load dfChart1Data that has all the project information
#   we will subset this to the corrent fund and exclude Closed Projects

# Thus, dfChart1Data  has ALL Project Data
#       dfChart1DataA has only Active Project Data

dfChart1Data <- subset(dfChart1Data, fundid == params$pFundID)
dfChart1Data <- droplevels(dfChart1Data)

dfChart1DataA <- subset(dfChart1Data, closed == "Active")
dfChart1DataA <- droplevels(dfChart1DataA)

# The Summary page will use the EHFX dataframe ...
if(params$pFundID == "EHF2")
  {dfEHFXTotals <- dfEHF2Totals} else {dfEHFXTotals <- dfEHF1Totals}

```


```{r label="f01_CreateChart", echo=FALSE}

# The Charting Function for Origination Charts (Line Charts)

f01_CreateChart <- function(dfdata,        # dataframe FROM f01_CreateChartData
                            ctitle,        # Chart Title
                            csubtext,      # Chart Subtitle
                            cflip=NULL,    # Fip the X & Y before charting
                            cCuml=NULL)    # Plot the Cumulative Balance
{ #Start of function
  
  # If the optional parameters were not provided, force them to FALSE
  if(is.null(cflip)) {cflip <- FALSE}
  if(is.null(cCuml)) {cCuml <- FALSE}
  
  # The "Chart_Total" column is 
  mySeries <- "Chart_Total"
  if(cCuml == TRUE) {mySeries <- "Chart_Cum"}
  
  theChart <- dfdata %>% 
  e_charts(x=Chart_X) %>% 
  e_title(text=ctitle,
          textStyle = list(fontSize=16),
          subtext=csubtext) %>% 
  e_line_(serie=mySeries) %>% 
 
  e_grid(right="15%") %>% 
  e_legend(orient="vertical",right="10", top="15%") %>% 
  e_tooltip(trigger="axis") %>% 
  e_toolbox_feature("saveAsImage")
  
  if(params$pFundID == "EHF2")
      {  
        theChart <- theChart %>% 
           e_legend(selector = list (
             list(type="inverse", title="Flip"),
             list(type="all", title="All")))
      }
  
  if(cflip == TRUE) {theChart <- theChart %>% e_flip_coords()}
  
  return(theChart) 
  
} # end of Function

```

```{r label="f02_CreateChart", echo=FALSE}

# The Charting Function for Active Assets (Bar Charts)

f02_CreateChart <- function(dfdata,        # dataframe FROM f01_CreateChartData
                            ctitle,        # Chart Title
                            csubtext,      # Chart Subtitle
                            cflip=NULL,    # Fip the X & Y before charting
                            cCuml=NULL)    # Plot the Cumulative Balance
{ #Start of function
  
  # If the optional parameters were not provided, force them to FALSE
  if(is.null(cflip)) {cflip <- FALSE}
  if(is.null(cCuml)) {cCuml <- FALSE}
  
  # The "Chart_Total" column is 
  mySeries <- "Chart_Total"
  if(cCuml == TRUE) {mySeries <- "Chart_Cum"}
  
  theChart <- dfdata %>% 
  e_charts(x=Chart_X) %>% 
  e_title(text=ctitle,
          textStyle = list(fontSize=14),
          subtext=csubtext) %>% 
  e_bar_(serie=mySeries,
         itemStyle = list(borderColor = "black", borderWidth = "1")) %>% 
  e_grid(right="15%") %>% 
  e_legend(orient="vertical",right="10", top="15%") %>% 
  e_tooltip(trigger="axis") %>% 
  e_toolbox_feature("saveAsImage")
  
  if(params$pFundID == "EHF2")
      {  
        theChart <- theChart %>% 
           e_legend(selector = list (
             list(type="inverse", title="Flip"),
             list(type="all", title="All")))
      }
   
  if(cflip == TRUE) {theChart <- theChart %>% e_flip_coords()}
  
  return(theChart) 
  
} # end of Function
```

```{r label="f01_CreateChartData", echo=FALSE}

f01_CreateChartData <- function (dfC1D,      # the dfChart1Data
                                 cX_Category,
                                 cY_Series,
                                 cActiveOnly)
{ # Start the Function
  
  # Later on, we will need to access the actual dataname referred to by these parameters
  cX_dataname  <- as.name(cX_Category)
  cY_dataname  <- as.name(cY_Series)
  
  # Select only Active Projects if ActiveOnly == TRUE
  dfC1Dx <- dfC1D
  if(cActiveOnly == TRUE) {dfC1Dx <- dfC1D %>% filter(closed == "Active")}

  # Drop any unused levels from dataframe factors
  dfSubtotals <- dfC1Dx %>% droplevels()
    
  # We create a dataframe with all the data for all builders
  # This will be used to plot the "Totals" line on our graphs
  # Yes - we are duplicating all of the data to do this!
  
  # create a new column called "chart_amount" duplicating the cY_series value
  # group the dataframe by the cX_Category
  # summarize and create a new dataframe with a new Chart_Total column
  #       -- this new column will be charted later on
  # then add in some cumulative totals for used in "cumulative" charts
  # then overwrite EVERY record with Total in the builder_3letter column
  dfSubtotals <- dfSubtotals %>% 
    mutate(chart_amount = {{cY_dataname}}, .before=project_id) %>% 
    group_by({{cX_dataname}}, .drop=FALSE)  %>% 
    summarize(Chart_Total = sum(chart_amount)) %>% 
    mutate(Chart_Cum   = cumsum(Chart_Total)) %>% 
    mutate(builder_3letter = "Total", .before={{cX_dataname}})
  
  # Now we will create a dataframe with the builder information
  # Notice we start with dfC1Dx which has been filterd for the relevant fund
  
  dfdata <- dfC1Dx %>% 
    filter(fundid == params$pFundID)
  
  #Drop the levels (as above)
  dfdata <- dfdata %>% droplevels()
  
  # This time group by builder_3letter AND the cX_Category
  # Note this dataframe has the identical column names as above
  #      --- that is IMPORTANT, I'll explain below
  dfdata <- dfdata %>% 
    mutate(chart_amount = {{cY_dataname}}, .before=project_id) %>% 
    group_by(builder_3letter, {{cX_dataname}})  %>%
    summarize(Chart_Total = sum(chart_amount), .drop=FALSE) %>% 
    mutate(Chart_Cum = cumsum(Chart_Total))
  
  # So now we are going to combine dfSubTotals and dfdata
  # This will give us the builder totals plus a "builder" called "Total"
  # In order to rbind these two dataframes, the layouts must be identical
  # Note: EHF1 only has LEN, so we don't need Totals
  if(params$pFundID == "EHF2") {dfdata <- rbind(dfdata,dfSubtotals)}
  dfdata <- rename(dfdata, Chart_X = {{cX_dataname}})
  dfdata <- arrange(dfdata,Chart_X)  
  
  # And now send the data back to be plotted
  return(dfdata)
  
} # end of Function
```

# Highlights {data-navmenu="Summary"}

## Column <!-- Column 1 -->

### <!-- Table: Number of Investments -->

```{r echo=FALSE}

flextable(data = dfEHFXTotals,
          col_keys = c("builder_3letter", "CountOrig","CountClosed", "CountActive"), 
          scrollable = TRUE) %>%
          add_header_row(top=TRUE, values="Origination Summary (Number of Investments)",colwidths=4) %>%         
          set_header_labels(
              builder_3letter = "Builder", 
              CountOrig       = "Originations", 
              CountClosed     = "Closed", 
              CountActive     = "Active") %>% 
          theme_vanilla() %>%         
          autofit()

```

### <!-- Chart: Committed Capital -->

       


```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D      =dfChart1Data,
                                               cX_Category ="f_OrigQtr",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  = "Number of Projects Closed by Quarter",
                 csubtext= NULL)
```


## Column <!-- Middle Column -->

### <!-- Table: Comitted Capital -->

```{r echo=FALSE}
flextable(data = dfEHFXTotals,
          col_keys = c("builder_3letter", "CostOrig","CostClosed", "CostActive", "ConBalActive")) %>% 
          add_header_row(top=TRUE, values="Comitted Capital (Project Cost)",colwidths=5) %>%
            set_header_labels(
              builder_3letter = "Builder", 
              CostOrig        = "Originations", 
              CostClosed      = "Closed",
              CostActive      = "Active",
              ConBalActive    = "Exposure") %>%         
              theme_vanilla() %>%         
              autofit()
```

      *  Closed - Project Cost on Closed Investments
      *  Active - Project Cost on Active Projects
      *  Exposure - Current Concentration Balance

### <!-- Chart: Concentration Balance -->

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_remain_term",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by Remaining Option Term",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

## Column <!-- Column 3 -->

### <!-- Table: Project Lots -->

```{r echo=FALSE}

flextable(data = dfEHFXTotals,
          col_keys = c("builder_3letter", "LotsOrig","LotsConveyClosed", "LotsConveyActive", "LotsActive")) %>% 
          add_header_row(top=TRUE, values="Reconciliation of Project Lots",colwidths=5) %>%
          set_header_labels(
              builder_3letter  = "Builder", 
              LotsOrig         = "Originations", 
              LotsConveyClosed = "Closed",
              LotsConveyActive = "Active",
              LotsActive       = "Unpurchased") %>% 
          theme_vanilla() %>%         
          autofit()
```

      *  Closed - Lots associated with Closed Projects
      *  Active - Lots conveyed on Active Projects
      *  Unpurchased - Lots owned by the Fund

### <!-- Chart: Unpurchased Lots by AVGSP -->

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_ASP",
                                               cY_Series   ="num_unpurchased.A",FALSE),
                 ctitle  ="Unpurchased Lots by the Project's Proforma WAVG ASP",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

# Supplemental {data-navmenu="Summary"}

## Column {.tabset}

### Poforma Revenue

```{r echo=FALSE}

flextable(data = dfEHFXTotals,
          col_keys = c("builder_3letter", "CountOrig","LotsOrig", "LandOrig", "ContractSumOrig",
                       "CostOrig", "LBMargin_Orig", "LBRev_Orig")) %>% 
          add_header_row(top=TRUE, values="Proforma Fund Revenue",colwidths=8) %>%
          set_header_labels(
              builder_3letter  = "Builder", 
              CountActive      = "Investments", 
              LotsOrig         = "Total Lots",
              LandOrig         = "Land Cost",
              ContractSumOrig  = "Site Cost",
              CostOrig         = "Project Cost",
              LBMargin_Orig    = "LB Margin",
              LBRev_Orig       = "Total Revenue") %>% 
          theme_vanilla() %>%         
          autofit()
```

# Investments {data-orientation=rows data-navmenu="Originations"} 

## Column {.tabset}

### $ByMonth

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D      =dfChart1Data,
                                               cX_Category ="f_OrigMth",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by Month",
                 csubtext='("000" omitted)')
```

### $ByQuarter

```{r echo=FALSE}

f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_OrigQtr",
                                               cY_Series   ="project_costs.P",FALSE),
                ctitle   ="Project Cost by Quarter",
                csubtext ='("000" omitted)')

```

### $Cumulative

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D      =dfChart1Data,
                                               cX_Category ="f_OrigMth",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Cumulative Project Cost by Month",
                 csubtext='("000" omitted)',cCuml = TRUE)
```

## Column {.tabset}

### #ByMth

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_OrigMth",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by Month",
                 csubtext='')
```

### #ByQtr

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D      =dfChart1Data,
                                               cX_Category ="f_OrigQtr",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by Quarter",
                 csubtext='')
```

### #Cumulative

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_OrigMth",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Cumulative Number of Projects Closed",
                 csubtext='', cCuml = TRUE)
```

### LotsByMth

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_OrigMth",
                                               cY_Series   ="num_lots",FALSE),
                 ctitle  ="Number of Lots Acquired by Month",
                 csubtext='')
```

### LotsByQtr

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D      =dfChart1Data,
                                               cX_Category ="f_OrigQtr",
                                               cY_Series   ="num_lots",FALSE),
                 ctitle  ="Number of Lots Acquired by Quarter",
                 csubtext='')
```

### LotsCumulative

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_OrigMth",
                                               cY_Series   ="num_lots",FALSE),
                 ctitle  ="Cumulative Number of Lots Acquired",
                 csubtext='', cCuml = TRUE)
```

# Project-Details {data-orientation=rows data-navmenu="Originations"}

## Column {.tabset}

### $ByBookStatus

```{r echo=FALSE}

f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_bookstatus",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by Book Status",
                 csubtext='("000" omitted)')
```

### $ByOptionTerm

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_optterm",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by Option Term",
                 csubtext='("000" omitted)')
```

### $ByASP

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_ASP",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by WAVG ASP",
                 csubtext='("000" omitted)')
```

## Column {.tabset}

### #ByBookStatus

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_bookstatus",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by Book Status",
                 csubtext='')
```

### #ByOptionTerm

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_optterm",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by Option Term",
                 csubtext='by Number of Projects')
```

### #ByASP

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_ASP",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by WAVG ASP",
                 csubtext='by Number of Projects')
```

# Compliance {data-orientation=rows data-navmenu="Originations"}

## Column {.tabset}

### $ByBuilder-Margin

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_hb_margin",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by Builder Margin",
                 csubtext='("000" omitted)')
```

### $ByLB-Margin

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_lb_margin.P",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by Land Bank Margin",
                 csubtext='("000" omitted)')
```

### $By1stTDown

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_1st_takedown.P",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by 1st Takedown Period",
                 csubtext='("000" omitted)')
```

### $ByHit70%

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_hit_70.P",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by Period Hit 70% Break Even",
                 csubtext='("000" omitted)')
```

## Column {.tabset}

### #ByBuilder-Margin

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_hb_margin",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by Builder Margin",
                 csubtext='("000" omitted)')
```

### #ByLB-Margin

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_lb_margin.P",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by Land Bank Margin",
                 csubtext='("000" omitted)')
```

### #By1stTDown

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_1st_takedown.P",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by 1st Takedown Period",
                 csubtext='("000" omitted)')
```

### #ByHit70%

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_hit_70.P",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by Period Hit 70% Break Even",
                 csubtext='("000" omitted)')
```

# Location {data-navmenu="Originations"}

## Column {.tabset}

### $ByMSATier 

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_msa_tier",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by MSA Tier",
                 csubtext=('"000" omitted'), cflip=FALSE)
```

### $ByState

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_state",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by State",
                 csubtext=('"000" omitted'), cflip=FALSE)
```

### $ByMSA

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_msa",
                                               cY_Series   ="project_costs.P",FALSE),
                 ctitle  ="Project Cost by MSA",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### #ByMSATier 

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_msa_tier",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by MSA Tier",
                 csubtext='')
```

### #ByState

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_state",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by State",
                 csubtext=('"000" omitted'), cflip=FALSE)
```

### #ByMSA

```{r echo=FALSE}
f01_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1Data,
                                               cX_Category ="f_msa",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Projects Closed by MSA",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

# Active Projects

## Column {.tabset}

### $ByBuilder

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_builder_3letter",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by Builder",
                 csubtext=('"000" omitted'), cflip=TRUE)

```

### $ByMSA_Tier

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_msa_tier",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by MSA Tier",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### $ByState

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_state",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by State",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### $ByMSA

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_msa",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by MSA",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### $ByRemainTerm

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_remain_term",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by Remaining Option Term",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### $ByASP

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_ASP",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by Proforma WAVG ASP",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### $ByHBMargin

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_hb_margin",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by Proforma Builder Margin",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### $ByLandBankMargin

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_lb_margin.P",
                                               cY_Series   ="cb_Qtr1",FALSE),
                 ctitle  ="Current Concentration Balance by Proforma Land Bank Margin",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

## Column {.tabset}

### #ByBuilder

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_builder_3letter",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by Builder",
                 csubtext=('"000" omitted'), cflip=TRUE)

```

### #ByMSA_Tier

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_msa_tier",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by MSA Tier",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### #ByState

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_state",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by State",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### #ByMSA

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_msa",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by MSA",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### #ByRemainTerm

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_remain_term",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by Remaining Option Term",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### #ByASP

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_ASP",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by Proforma WAVG ASP",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### #ByHBMargin

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_hb_margin",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by Proforma Builder Margin",
                 csubtext=('"000" omitted'), cflip=TRUE)
```

### #ByLandBankMargin

```{r echo=FALSE}
f02_CreateChart(dfdata   = f01_CreateChartData(dfC1D       =dfChart1DataA,
                                               cX_Category ="f_lb_margin.P",
                                               cY_Series   ="w_recordcount",FALSE),
                 ctitle  ="Number of Active Projects by Proforma Land Bank Margin",
                 csubtext=('"000" omitted'), cflip=TRUE)
```







