---
title: "Project Summaries"
author: ''
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[LO,LE]{EHF Project Updates}
  - \fancyhead[RO,RE]{Confidential}
  - \fancyfoot[CO,CE]{For Internal Use Only}
  - \fancyfoot[RE,RO]{\thepage}
  - \usepackage[T1]{fontenc}
geometry: "left=2cm,right=2cm,top=3cm,bottom=2cm"
fontsize: 12
output:
  pdf_document:
    toc: yes
    number_sections: true
    df_print: kable
    latex_engine: xelatex
  html_document:
    toc: yes
    toc_float: no
    number_sections: yes
    theme: simplex
  word_document:
    toc: yes
    number_sections: true
    df_print: kable
---

```{=html}
<style type="text/css">
 body { 
   font-family: "Source Sans Pro", sans-serif; 
   font-size: 14px;
 }
 h1.title {
   font-size: 20px;
 }
 td {  /* Table  */
   font-size: 14px;
 }
 h1 { /* Header 1 */
   font-size: 14px;
   font-weight: bold; 
   
 }
 h2 { /* Header 2 */
   font-size: 14px;
   font-weight: bold; 
 }
 h3 { /* Header 3 */
   font-size: 16px;
   font-weight: bold; 
 }
 blockquote { /* BlockQuote */
   font-size: 14px;
   color: DarkBlue;
 </style>
```
```{=html}
<style type="text/css">
.main-container { /* dynamically fill window */
  max-width: 100% !important;
  margin: auto;
}
</style>
```
```{r include=FALSE, label="setup"}

# If you want to flip the report to landscape, insert this before geometry in YAML Header
# classoption: landscape

# R Package Definitions                                       
library(tidyverse)
library(lubridate)
library(tidyquant)  
library(dplyr)
library(scales)
library(forcats)
library(ggrepel)
library(openxlsx)
library(flextable)
library(tinytex)
library(knitr)
library(kableExtra)
library(rmarkdown)

# knitr global options
knitr::opts_chunk$set(echo = FALSE, error=FALSE)
options(dplyr.summarise.inform = FALSE)

```

```{r include=FALSE, label="setup-input-filenames"}

rm(list = ls())

# Project Directory
myDirectory <- "~/Dropbox/Board Package Material/CC R Portfolio"

# The Project Files
idf_ProjAll      <- paste0(myDirectory,"/03 df Files/dfProjAll.rda")

# Load dfProjAll
load(idf_ProjAll)

```

```{r GetProjectDetails, echo=FALSE}

f01_GetProjectDetails <- function(project_lookup) {
 
# retreive the Project   
dfstart <- dfProjAll %>% subset(project_id == project_lookup)

dftemp <- dfstart %>% 
  select(c(Fund          = "fundid",
           Builder       = "builder_3letter",
           Project       = "proj_name",
           Acquisition   = "book_status",
           City          = "city",
           State         = "state",
           MSA           = "msa")) %>% 
  as.list() %>% 
  enframe(name="Name1", value="Value1") %>% 
  rownames_to_column("Index")

dftemp2 <- dfstart %>% 
  mutate(project_costs.P = dollar(project_costs.P)) %>% 
  mutate(hb_margin_percent = (hb_margin_percent)) %>% 
  mutate(cb_Qtr1         = ifelse(is.na(cb_Qtr1),dollar(0),dollar(cb_Qtr1))) %>% 
  select(c(NbrOfLots         = "num_lots",
           NbrOfLotTypes     = "num_lot_types",
           UnpurchasedLots   = "num_unpurchased.A",
           FinalTDown        = "lots_in_final_tdown.A",
           ProjectCost       = "project_costs.P",
           Concentration     = "cb_Qtr1",
           HB_Margin         = "hb_margin_percent")) %>% 
  as.list() %>% 
  enframe(name="Name2", value="Value2") %>% 
  rownames_to_column("Index")

dftemp3 <- dfstart %>% 
  mutate(d_term_start        = format(d_term_start)) %>% 
  mutate(d_term_end          = format(d_term_end)) %>% 
  select(c(LB_COE            = "d_term_start",
           Option_Term       = "opt_term",
           RemainingMths     = "remain_term",
           OptionEnds        = "d_term_end",
           FirstTDownMth     = "first_takedown_period.P")) %>% 
  as.list() %>% 
  enframe(name="Name3", value="Value3") %>% 
  rownames_to_column("Index")

dfFinal <- merge(x=dftemp,y=dftemp2,by="Index",all=TRUE)
dfFinal <- merge(x=dfFinal,y=dftemp3,by="Index",all=TRUE)
dfFinal <- dfFinal %>% select(-c(Index))
dfFinal[is.na(dfFinal)] <- " "

# Now build and return the Presentation Table
kbFinal <- knitr::kable(dfFinal, col.names = NULL, booktabs=T, linesep = "") %>%
          kable_styling(full_width = T) %>%
          column_spec(c(3,5), width = "2.5cm", color = "blue", bold = F) %>% 
          column_spec(1, width = "1.5cm", color = "blue", bold = F)

return(kbFinal)

}

```


\pagebreak 

# EHF1 Watchlist Project Updates 
   

## **Russell Ranch**\ 
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 139)
kbInfo

```
**Next Steps**\      
 - Project is expected to close out in Jun2024     


**Sales/Market**\     
 - Sales have been slightly behind proforma.  However, LEN reports 51 net sales in Oct2023 which is well above the target pace of 4/mo per product type.       
 - Traffic has been strong and Russel Ranch is one of the best selling markets in the area     
 - LEN is offering rate buydowns and seller paid closing costs to move product  


\pagebreak   

##  **Greenwood**\          
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 316)
kbInfo

```    
**Background**\     
 - The project is being entitled and developed in five phases (631 total lots; 6 product types)     
 - The Final Plats record prior to Substantial Completion of the Lots     
 - LEN Land Banked Phases 1-3; 5-6     
 - LEN retained Phase 4 Lots; sales were underway prior to the Land Bank COE     
 - All Final Maps are recorded (+/-10 months behind proforma and first takedown date)     
 - Phase 5 (146 lots): The Lots are Substantially Complete     
 - Phase 3 (90 lots):  The Lots are Substantially Complete       
 - Phase 6 (97 lots):  The Lots are Substantially Complete (+/-9 months behind proforma and first takedown date)     
 - The project is on the IC List for entitlement and substantial completion delays     

**Development**\     
 - Phase 1 (159 lots):  Site work and is expected to start in early 2024, with Substantial Completion in Nov2024 (+/-10 months behind proforma and first takedown date for those Lots)  
 - Phase 2 (138 lots):  Site work expected to start in late 2024; with Substantial Completion in mid 2025 (+/-18 months behind proforma and first takedown date for those Lots).  Substantial completion for this phase of lots is expected after the Option End date   

**Sales Commencement**\     
- The Community is open for sales (5 months ahead of proforma sales commencement date); utilizing models from Phase 4
- However, LEN reports this Division is a 100% spec builder and will not sale until the home is nearing completion

**Sales/Market**\     
- Len reports 3 net sales in Nov2023
- Sales price Incentives up to $40K per home
- LEN offers rate buydown to 4.5% - 7/6 ARM
- LEN pays 4% of closing costs

**Next Steps**\     
 - The Community is on the IC List and will be monitored closely for substantial completion progress.   
 - It is projected that the Phase 2 lots will not be substantially complete until just prior to the Option End Date     
 - The Team will seek IC approval to allow LEN to continue acquiring unfinished lot inventory throughout the balance of the Option Term     

\pagebreak 

## **Legacy Village**\     
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 340)
kbInfo

```    
**Background**\     
 - The Final Map was recorded prior to COE      
 - The Project was developed in 2 phases      
 - Phase 1 (125 lots):  The Phase 1 lots are Substantially Complete (2 months behind proforma and first takedown date)     
 - Phase 2 (100 lots):  The Phase 2 lots are Substantially Compete (consistent with proforma and first takedown date)     
 - Offsite and District Improvements are Substantially Complete      
 - The Community is open for sales consistent with proforma sales commencement date     

**Sales and Market**\     
 - Overall sales over proforma for the Quarter.     
 - ASP above proforma by 8%.     

**Next Steps**\     
 - Continue with routine Project Reviews     

\pagebreak 

## **Lorraine Lakes**\     
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 363)
kbInfo

```
**Background**\    
 - The project is being entitled and developed in sixteen phases (884 total lots; 5 product types)      
 - All Final Plats are recorded (+/-6 months behind proforma and first takedown dates for the individual Phases)     
 - Lots are Substantially Complete in fourteen of the development phases (723 total lots; “A” = 151; "B" = 156; "C" = 80; "D" = 180 & "E" = 156 lots)     
 - The Community is open for sales (consistent with proforma and sales commencement date)     
 - The project is on the Watch List for substantial completion delays (up to 8 months behind proforma and first takedown dates for Phase 2)     

**Remaining Development**\			
 - Phase 2C-3 ("B" = 69 lots):  The Lots are expected to be Substantially Complete in Mar2024 (+/-2 months behind proforma and first takedown date for these lots)    
 - Phase 2C-4 ("A" = 83 & "B" = 9 lots):  The Lots are expected to be Substantially Complete in May2024 (+/-5 months behind proforma and first takedown date for these lots)    
 - LEN reports early delays in sourcing materials needed to complete the work for the remaining phases   
 - Only one of the remaining phases are expected to have delays in substantial completion of more than 5 months    

**Sales/Market**\		
 - Overall sales exceeding proforma for the Quarter 	 		
 - Overall ASP over proforma by 17%     

**Watch List Comments**\     			
 - The project has been on the Watch List due to ongoing development delays.  
 - While LEN has experienced an eight-month delay in achieving substantial completion for Phase 2C-2 the lots are now Substantially Complete      

\pagebreak 

## **Middle Vistas**\        
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 209)
kbInfo

```
**Background**\      
 - The project is being entitled and developed in one phase (228 lots; 2 product types)     
 - The Final Plat was recorded prior to COE     
 - The Lots are now Substantially Complete (17 months behind proforma and first takedown date)     
 - LEN has reported delays were due to utility borings that needed to be done under a BLM owned canal and plan approvals      
 - LEN has been taking down unfinished lots since May2022      
 - The project is on the Watch List for substantial completion and sales commencement delays      

**Sales/Market**\      
 - The Community is now open for sales (+/-10 months behind proforma sales commencement date)     
 - A Model completion is expected in Mar2024     
 - As of December there had been no sales for the A Lots/Discovery Collection and a total of 5 B/Horizon units.     
    - Sales for both lots types just opened.     
 - LEN is targeting a pace of 4 per month     
 - LEN is not offering any price concessions at this time, but offering buydowns and seller paid closing costs     
	
**Watch List Comments**\    
 - The project has been on the Watch List due to extended development and Sales Commencement delays      
 - However, LEN has been acquiring partially completed lots consistent with the Lot Takedown schedule up until Oct2023.        
 - The lots are now substantially complete, and sales have commenced       

**Next Steps**\    
 - Continue to monitor sales and the completion of the models      
 - Continue with routine Project Reviews      

\pagebreak 

## **Pioneer Village**\   
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 211)
kbInfo

```
**Background**\     
 - The project was entitled and developed in one phase (231 total lots; 2 product types)          
 - The Final Map is recorded (2 months behind proforma and first takedown date)     
 - The Lots are Substantially Complete (2 months behind proforma and first takedown date)     
 - The Community is open for sales (+/-10 months behind proforma sales commencement date)     
 - Proforma plan was to pre-sell while the models were under construction; however, due to the change in market conditions     
 - LEN changed the sales strategy to start sales after the models were complete and open       
 - The Community is on the Watch List for sales commencement delays     

**Sales/Market**\     
 - LEN reports strong traffic and interest in this community     
 - LEN's strategy is to have consistent starts, sales and closings.       
 - They are marketing to local and Bay area buyers, looking for affordability     
 - LEN is offering rate buydowns and seller paid closing costs     
 - Current sales pace is 4/mo per product type.  
 - LEN is on target with the sales pace for Sep2023 and Oct2023     

**Next Steps**\          
 - While the project has been on the Watch List due to an extended Sales Commencement delay, it is now open for sales     
 - There is no remaining risk of future Development Strategy delays as all lots are substantially complete and the Final Map is recorded               

\pagebreak 

## **Russell Ranch**\       	
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 139)
kbInfo

```
**Background**\      	
 - The Project was entitled and developed in two phases (513 total lots; Phase 1 = 242 & Phase 2 = 271 lots)             
 - The Final Map records prior to substantial completion of the lots     
 - The Final Maps are recorded (consistent with proforma and first takedown date)     
 - The Phase 1 Lots are Substantially Complete (2 months behind proforma and first takedown date)     
 - The Phase 2 lots are complete including energizing the lift station (+/-8 months behind proforma and first takedown date)     
 - The Community is open for sales with completed models (consistent with proforma and first takedown date)     
 - The Community was on the Watch List for substantial completion of the Phase 2 Lots     

**Sales/Market**\     
 - Sales have been slightly behind proforma.  However, LEN reports 51 net sales in Oct2023 which is well above the target pace of 4/mo per product type.       
 - Traffic has been strong and Russel Ranch is one of the best selling markets in the area     
 - LEN is offering rate buydowns and seller paid closing costs to move product     

**Next Steps**\         
 - All Final Maps are recorded, all lots are substantially complete, and the Community is open for sale     
 - Continue with routine Project Reviews

\pagebreak 

## **Walnut Creek**\            	
```{r echo=FALSE}

kbInfo <- f01_GetProjectDetails(project_lookup = 158)
kbInfo

```
**Background**\     
 - The 367-Lot Property includes seven entitlement and development phases, of which six were substantially complete with recorded Final Plats at the COE     
 - The Final Map records after substantial completion of each development phase     
 - While the site improvements for these last lots are complete, LEN needs to fill in some basin swells & stabilize the surrounding areas before this seventh phases will be considered substantially complete      
 - Since there are 22 lots in the Final Phase not impacted by the incomplete basins, LEN opted to submit a revised Final Plat, which Recorded in late Aug2023 (+/-3 months behind proforma and takedowns for those lots)  
 - The Community is open for sales (ahead of proforma sales commencement date)  

**Entitlement/Development**\     
 - There are 27 Land bank lots remaining to be platted and recorded (All "A" Lots)     
 - The basin-related work is expected to be complete in Dec2023 (+/-6 months behind proforma), at which time 9 more lots will be ready to Record      
 - The Final 18 lots are not expected to Record until Oct2024, as these sediment basins require all home construction upstream to be 100% complete to deem the lots complete     
 - Therefore, the last 18 lots are not expected to have a Recorded Plat prior to the Option end date of Mar2024      
  
**Impact on Lot Takedowns**\     
 - Based on the above schedule, the project is expected to be on plat delay in Nov2023-Dec2023, and starting in Feb2024 will not have the last 17 lots platted until after the Option End date       

**Sales/Market**\
 - Final take down scheduled for MAR2024     
 - ASP over 49% of proforma     

**Next Steps**\     
 - The Community is on the IC List, and will not have enough platted lots to takedown in Mar2024 - Option End Date     
 - LEN plans to acquire the remaining 18 lots via a metes and bounds survey in Mar2024     
     		
\pagebreak 

